### 2014-04-01 paper/relatedwork.tex
related work design space

\section{Related Work}
Our contributions relate to other efforts to add interactivity to digitally fabricated objects; and to techniques for routing and model modification.

@@

Previous work has investigated the integration of interactivity with the fabrication process.  Printed Optics (\cite{Willis-printedoptics}) used light pipes, solid clear tubes, to create integrated displays and touch sensors: our work is inspired by this and goes towards a design tool for these capabilities.  Slyper, et al., in \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  This technique is complementary to ours, as we allow placing these interactive elements anywhere on an object's surface; they had to place them in locations accessible for electronics insertion. Acoustic Barcodes explored integrating ridges into fabricated objects, whose acoustic signatures when scraped provided an ID code \cite{Harrison-acoustic}; while pipes can be used for identification and to create aural feedback, this is not our only goal.  Sauron investigated computer vision to track interactions with physical mechanisms \cite{Savage-sauron}.  While Savage, et al., used mirrors for redirection, we believe that the required line-of-sight operation for their computer vision techniques may be possible using printed optics or inserted optical fibers.  General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in Midas \cite{Savage-midas}.  This technique, based on circuitboard routing, is limited to planar and unfoldable shapes, and intended for use on the surface of objects rather than through their cores.  Fabrickation works towards rapid fabrication of functional objects by integrating construction kit building blocks \cite{Mueller-fabrickation}.  While we recognize that 3D printing requires significant time, we believe creating precise internal structures in 3D printed objects is a strong case for digital fabrication over manual or traditional methods.

@@

Other research has brought traditional electronics to 3D prints.  Sells, et al., \cite{Sells-reprap}, describe using a heated syringe to deposit metal in printed 2D circuitboard channels on objects' surfaces.  Sarik, et al., \cite{Sarik-tracebrush} and the Optomec company \cite{optomec} describe \emph{spraying} conductive material onto objects to create circuitry.  Injection of liquid metals for sensing in softer-than-skin electronics was explored by Park, et al., \cite{Park-microchannels} and Majidi, et al., \cite{Majidi-curvature}.  Navarette, et al., created a functioning GPS routed in true 3D (not multilayer boards' 2.5D), hand-built using a one-off routing.  Our work differs from these because we offer \emph{algorithms and techniques} for \emph{internal}, \emph{true 3D} routing.

@@

Other researchers are investigating interaction for fabrication (i.e., interaction techniques for controlling digital fabrication machines) rather than fabrication for interaction as we do.  This includes work like Constructable \cite{Mueller-constructable}, KidCAD \cite{Follmer-kidcad}, and Willis, et al,'s interactive interfaces \cite{Willis-interactive}. Their contributions are orthogonal to ours.

@@

There is prior work on modeling the interior of objects (as opposed to their exterior).  In Make it Stand, material is removed from the interior of objects with the goal of changing their center of gravity \cite{Prevost-makeitstand}.  Bickel, et al., explored enforcing deformation behavior with material blending \cite{Bickel-deformation}, while B\"{a}cher, et al., built an algorithm for automatically placing 3D fabricatable joints into meshes \cite{Bacher-articulated}.  Takayama, et al., built a system described in \cite{Takayama-fruit} which allowed users to create internal color maps of the interior of objects, allowing them to see digital ``slices'' of their ``oranges.''  Sauron automatically modified the interior of existing mechanical objects to make them amenable to vision-based sensing \cite{Savage-sauron}, and Infrastructs created encoded interior cavities in 3D printed objects designed to be sensed with a terahertz imaging tool.  All these contributions are orthogonal to ours, as our focus is on modeling pipes and hollow chambers for fabricating interactive objects.

>>>>

\section{Related Work}\tovi{related work section still needs some work}
Our contributions relate to other efforts aiming to add interactivity to digitally fabricated objects; and to techniques for routing and model modification.

@@

Previous work has investigated the integration of interactivity with the fabrication process.  Printed Optics (\cite{Willis-printedoptics}) used light pipes, solid clear tubes, to create integrated displays and touch sensors. The describes a process, but does not provide a design tool for creating such objects. Our work is inspired by Printed Optics and introduces a design tool for modelling objects that can have these types of capabilities.

\tovi{dont use citations as nouns}
Slyper, et al., in \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  \tovi{clean up writing - finish telling the reader what they did or didnt do, then respond with what we do differently}This technique is complementary to ours, as we allow placing these interactive elements anywhere on an object's surface; they had to place them in locations accessible for electronics insertion. \tovi{not sure this is relevant enough to cite here}Acoustic Barcodes explored integrating ridges into fabricated objects, whose acoustic signatures when scraped provided an ID code \cite{Harrison-acoustic}; while pipes can be used for identification and to create aural feedback, this is not our only goal.  Sauron investigated computer vision to track interactions with physical mechanisms \cite{Savage-sauron}.  While Savage, et al., used mirrors for redirection, we believe that the required line-of-sight operation for their computer vision techniques may be possible using printed optics or inserted optical fibers.

General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in Midas \cite{Savage-midas}.  This technique, based on circuitboard routing, is limited to planar and unfoldable shapes, and intended for use on the surface of objects rather than through their cores.  Fabrickation works towards rapid fabrication of functional objects by integrating construction kit building blocks \cite{Mueller-fabrickation}.  While we recognize that 3D printing requires significant time, we believe creating precise internal structures in 3D printed objects is a strong case for digital fabrication over manual or traditional methods.

@@

Other research has investigated the integration of traditional electronics into 3D prints.  Sells, et al., \cite{Sells-reprap}, describe using a heated syringe to deposit metal in printed 2D circuitboard channels on objects' surfaces.  Sarik, et al., \cite{Sarik-tracebrush} and the Optomec company \cite{optomec} describe \emph{spraying} conductive material onto objects to create circuitry.  Injection of liquid metals for sensing in softer-than-skin electronics was explored by Park, et al., \cite{Park-microchannels} and Majidi, et al., \cite{Majidi-curvature}.  Navarette, et al., created a functioning GPS routed in true 3D (not multilayer boards' 2.5D), hand-built using a one-off routing.  Our work differs from these because we offer \emph{algorithms and techniques} for \emph{internal}, \emph{true 3D} routing.   \tovi{relation of this stuff to ours isn't so clear}

@@

Other researchers are investigating interaction for fabrication (i.e., interaction techniques for controlling digital fabrication machines) rather than fabrication for interaction as we do.  This includes work like Constructable \cite{Mueller-constructable}, KidCAD \cite{Follmer-kidcad}, and Willis, et al,'s interactive interfaces \cite{Willis-interactive}. Their goals and contributions are orthogonal to ours.

@@

There is prior work on modeling the interior of objects (as opposed to their exterior).  In Make it Stand, material is removed from the interior of objects with the goal of changing their center of gravity \cite{Prevost-makeitstand}.  Bickel, et al., explored enforcing deformation behavior with material blending \cite{Bickel-deformation}, while B\"{a}cher, et al., built an algorithm for automatically placing 3D fabricatable joints into meshes \cite{Bacher-articulated}.  Takayama, et al., built a system described in \cite{Takayama-fruit} which allowed users to create internal color maps of the interior of objects, allowing them to see digital ``slices'' of their ``oranges.''  Sauron automatically modified the interior of existing mechanical objects to make them amenable to vision-based sensing \cite{Savage-sauron}, and Infrastructs created encoded interior cavities in 3D printed objects designed to be sensed with a terahertz imaging tool.  All these contributions are orthogonal to ours, as our focus is on modeling pipes and hollow chambers for fabricating interactive objects.   \tovi{need better summary statement instead of ``all of this is orthogonal''}
